Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
table of spread

>>>>

\subsection{TOGGLE\_SPAGHETTI (Combinatorial toggles)}

\begin{table}[ht]
\caption{Combinatorial Toggle Smell}
\centering
\begin{tabular}{|p{1.3cm}|p{7cm}|}
 \hline\hline
 Description & This smell is observed when the execution of code is controlled by combination of states of several toggles.  \\ \hline 
 Example &  
 \begin{lstlisting} 
 	//Location: /chrome/browser/about_flags.cc (taken from Google chrome)
void FlagsState::
ConvertFlagsToSwitches(FlagsStorage* flags_storage, 
base::CommandLine* command_line, SentinelsMode sentinels) {
if (command_line->
HasSwitch(switches::kNoExperiments))
return;

std::set<std::string> enabled_experiments;
//FlagsForCurrentPlatform = FFCP
GetSanitizedEnabledFFCP
(flags_storage, &enabled_experiments);

NameToSwitchAndValueMap name_to_switch_map;
for (size_t i = 0; i < num_experiments; ++i) {
const Experiment& e = experiments[i];
if (e.type == Experiment::SINGLE_VALUE) {
	SetFlagToSwitchMapping(
	e.internal_name, e.command_line_switch,
	e.command_line_value, &name_to_switch_map
	);
} else if (e.type == Experiment::MULTI_VALUE) {
		for (int j = 0; j < e.num_choices; ++j) {
		SetFlagToSwitchMapping(
		e.NameForChoice(j),
		e.choices[j].command_line_switch,
		e.choices[j].command_line_value,
		&name_to_switch_map
		);
	}
	} else {
		DCHECK_EQ(e.type,
		Experiment::ENABLE_DISABLE_VALUE);
		SetFlagToSwitchMapping(
		e.NameForChoice(0), std::string(), std::string(),
		&name_to_switch_map
		);

		SetFlagToSwitchMapping(
		e.NameForChoice(1), e.command_line_switch,
		e.command_line_value, &name_to_switch_map
		);
		SetFlagToSwitchMapping(
		e.NameForChoice(2), e.disable_command_line_switch,
		e.disable_command_line_value, &name_to_switch_map
		);
		}
	}
}

 \end{lstlisting}
 \\ \hline

 Possible reasons for their presence & 
 \begin{enumerate}
\item Mix of canary use cases or A/B testing in toggle block could result in this kind of spaghetti code.
\item Inconsistency in API’s used to manage toggles and canary use cases.
\item Presence of more than one API to manage feature flags. Transition from legacy feature toggles to more formal one.
\end{enumerate}

  \\ \hline
 Name & TOGGLE\_DEAD \\ \hline
 Name & TOGGLE\_DEAD \\ \hline
 Name & TOGGLE\_DEAD \\ \hline

\end{tabular}
\label{table:chrome-dir-data}
\end{table}
